Thermodynamic fragments in magic state theories

### 2020-07-21 magic_paper.tex
Started noisy subsection

@@

@@

Clearly by definition, 
\begin{align}
	\Phi_+(2m+1;n,p) &= \Phi_+(2m;n,p), \\
	\Phi_-(2m;n,p) &= \Phi_-(2m-1;n,p),
\end{align}
so we define the piece-wise functions
\begin{equation}
	L(m;n) =
	\begin{cases}
	L_+(m; n),&\ m\text{: even}, \\
	L_-(m; n),&\ m\text{: odd}
	\end{cases}
\end{equation}
and
\begin{equation}
	x(m;n) =
	\begin{cases}
	x_+(m; n),&\ m\text{: even}, \\
	x_-(m; n),&\ m\text{: odd}
	\end{cases}
\end{equation}
Finally, the $m$-th elbow is located at
\begin{equation}
	\left(x_m, \lc{\ketbra{\rm{S}}^{\otimes n}}{\frac{1}{d}\id}(m) \right) = \left( x(2m;n), L(2m;n) \right),
\end{equation}
where $2m$ is considered \hspace{-7pt}$\mod{(n+1)}$.

@@

>>>>

\subsubsection{Lorenz curve ordering and maximum}

@@

\subsubsection{Lorenz curve in terms of a binomial cumulative distribution}

@@

Clearly by definition, 
\begin{align}
	\Phi_+(2m+1;n,p) &= \Phi_+(2m;n,p), \\
	\Phi_-(2m;n,p) &= \Phi_-(2m-1;n,p),
\end{align}
so we define the piece-wise functions
\begin{equation}
	L(m;n) =
	\begin{cases}
	L_+(m; n),&\ m\text{: even}, \\
	L_-(m; n),&\ m\text{: odd}
	\end{cases}
\end{equation}
and
\begin{equation}
	x(m;n) =
	\begin{cases}
	x_+(m; n),&\ m\text{: even}, \\
	x_-(m; n),&\ m\text{: odd}
	\end{cases}
\end{equation}
Finally, the $m$-th elbow is located at
\begin{equation}\label{eq:slc}
	\left(x_m, \lc{\ketbra{\rm{S}}^{\otimes n}}{\frac{1}{d}\id}(m) \right) = \left( x(2m;n), L(2m;n) \right),
\end{equation}
where $2m$ is considered \hspace{-7pt}$\mod{(n+1)}$.

\subsubsection{Bounds on cumulative distribution}

@@

\subsubsection{Noisy Strange states}

Strange states of the form 
\begin{equation}
    \rho_{\rm{S}}(\epsilon) = (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \frac{1}{d}\id,
\end{equation}
contain two discrete Wigner components, so $n$-copy states $\rho_{\rm{S}}^{\otimes n}(\epsilon)$ contain $n+1$ discrete components~\cref{tab:swc} as in the noiseless case.
\begin{table}[h]                           
 \centering
 \begin{tabular}{|c|c|}
 \hline
 $m_j$ & $8^{n-j}\binom{n}{j}$ \\ [0.5ex] 
 \hline\hline
 $w_j$ & $\left(\frac{1}{6} - \frac{1}{18}\epsilon \right)^{n-j}\left(-\frac{1}{3} + \frac{4}{9}\epsilon \right)^{j}$ \\
 \hline
\end{tabular}
 \caption{Wigner components of $\rho_{\rm{S}}^{\otimes n}(\epsilon)$}
 \label{tab:swc}
\end{table}

Clearly, there are negative Wigner components iff $0\leq \epsilon < \frac{3}{4}$.
At the limiting case of non-negative Wigner components $\epsilon = \frac{3}{4}$, the Lorenz curve is simply given by three points,
\begin{equation}
\left\{(0,0), \left(\left(\frac{8}{9}\right)^n, 1\right), (1,1) \right\}
\end{equation}
and exponentially tends to a step-function.
The case of $\epsilon = 0$ is given at~\cref{eq:slc} and the noisy cases with $0 < \epsilon < \frac{3}{4}$ follow a similar analysis.
